The responses of \textit{\textit{Spinifex littoreus}} to sand burial on the coastal area of Pingtan Island, Fujian Province, South China

### 2021-01-01 tex/interactcsesample.tex
rectified according Du's comments -v3

\documentclass[]{interact}

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required

@@

\articletype{ARTICLE}% Specify the article type or omit as appropriate

@@

\begin{abstract}
\label{abstract}
% 砂生植物对沙埋藏的适应能力对海岸沙丘系统的生态恢复至关重要。
The adaptive capacity of psammophytes to sand burial is crucial for the ecological restoration of coastal dune systems. 
% 研究了福建平潭岛海岸滨鹬对不同埋沙深度和埋沙深度的响应。
The responses of \textit{Spinifex littoreus} to different sand burial depths and levels were examined on the coast of Pingtan Island, Fujian Province, South China. 
% 结果表明，与对照组相比，砂埋对其匍匐茎的垂直生长无显著影响。
The results indicated that, compared with the control group (CG), sand burial on the \textit{S. littoreus} stolons had no significant impact on the vertical growth of its conjoint ramets. 
% 然而，随着砂埋的继续，匍匐茎顶端生长更快，完全砂埋比半砂埋影响更明显。
However, the horizontal growth of \textit{S. littoreus} stolons were stimulated and significantly increased in half-intense (HI) and complete-intense (CI) sand burial treatments by 24.56\% and 40.79\%, respectively. 
% 在不定根和叶片上，三个匍匐茎上的干生物量分配均发生了变化，而在茎上则没有变化。
Throughout the experiment, about 96\% of adventitious roots were observed on the base section of stolons, while no roots in the control group (CG). 
After a 20-day artificial sand burial treatments, the dry weight ratio between stem and leaf of \textit{S. littoreus} was decreased in all three sections of stolons, especially for the top sections. 
% 通过匍匐茎的快速生长，匍匐茎基部产生大量不定根，匍匐茎顶端的叶片萌发率较高，可以适应完全的砂埋。
Overall, \textit{S. littoreus} can adapt to the complete and intense sand burial in growing season by rapid growth of stolons, abundant production of adventitious roots on the stolon base, and more germination of leaves on the stolon top.
\end{abstract}

@@

\subsection{Methods}
Field experiments were carried out in July, 2016, in Tannan bay, Pingtan Island (Figure~\ref{fig:map}). One study belt without the interruption of animals, pollutants, and apparent human activities was selected in the center of the coastal sand dunes. 
Considering most of the \textit{S. littoreus} were distributed on the windward slope of nebkhas in mobile dunes belt, 35 healthy plants with uniform size were selected for study on this slope (Figure\ref{fig:leeward_swale}). All the observed plants can be well distinguished from surrounding plants, the height of vertical ramets and the length of stolons were all similar with each other before the burial treatments. Stolons of \textit{S. littoreus} on the windward slopes were selected, and labeled with a red cord at points 1/3 and 2/3 of the length from the stem base to the top of the stolons. All plant species around the selected plants around the selected plants were manually cleared, and wooden frames $20 cm$ in height (similar to the height of stolons) were set around the selected plants. Later, all the observed plants were fixed with a label, and its serial number was recorded on the label and wooden baffles respectively in order to facilitate the periodic measurements later. The few adventitious roots present on the stolons of the observed plants were completely eliminated, the height of vertical ramets and length of stolons were measured separately before the experiments began. Later, all the plants were buried with sand nearby artificially (Figure~\ref{fig:diagram}, Table~\ref{tab:treatment}), While control groups (CG) were unburied throughout the experiments.

@@

Since the vertical ramets of \textit{S. littoreus} is relatively high, it is unlikely for them to be completely buried in single typhoon event (Figure~\ref{fig:sample-pic}a). The treated \textit{S. littoreus}, thus, only the stolons of which were buried at different depths and levels (see Figure~\ref{fig:diagram} and Table~\ref{tab:treatment}). Moreover, some adventitious roots on the stolons of selected plants were observed only a few days after treatments, so the growth parameters of plants were dynamically investigated in 5, 9, 13, 17, 20 days after the sand burial to investigate the response of \textit{S. littoreus} to severe sand burial over a short time scale.

@@

Consequently, the rapid growth of ramets height in \textit{S. littoreus} is not considered as the priority for the escape of sand burial, but it inclines to increase the stolon length due to its vulnerability to be buried in a typhoon event, which may contribute to the no significant impact on the ramets height by artificial sand burial tin our experiment \citep{maunAdaptationsEnhancingSurvival1994}. Our field investigation further showed that the maximum length of \textit{S.littoreus} stolons could be up to $2-3 m$, which was about to 4-6 times of its ramets height in a frequent sand burial habitat (Figure~\ref{fig:added}b). This is in agreement to the previous study from \citet{woodhouseEffectSpeciesDune1977}, who reported that \textit{Uniola paniculata} tended to grow upward rather than seaward, while \textit{Ammophila breviligulata} preferred to colonize seaward beach surfaces by rhizome growth, which may explain the wider distribution of the latter in an intensive sand burial environment subsequently.

\begin{figure}[!h]
  \centering
  \subfloat[Developmental period.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9a.jpg}}}\hspace{5pt}
  \subfloat[Stabilized period.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9b.jpg}}}
  \caption{The stolon length of \textit{S. littoreus} on nebkhas in the developmental period (a) and the stabilized period (b). (Photo by Pingtan Island)} 
  \label{fig:added}
\end{figure}

Extensive colonization of horizontal stolons after sand burial will facilitate the plants to increase its capacity for utilization of water and nutrition, which is especially critical for the establishment of plants in a resource-poor environment, such as coastal sand dunes, and further enhance their growth as the dominant species in coastal sand dunes \citep{divyasreeEcologicalStudyReproduction,mendoza-gonzalezBiologicalFloraCoastal2014}. Our results indicated that all sand burial treatments had a significant promotion on the  stolon growth, and complete sand burial had more obvious influence than half sand burial. Species usually stimulate their growing point according to the signal of the gravity signal stresses \citep{zhouAnalysisgrowthstrategy2015}, and increase their node number and internode length to escape this physical barrier \citep{maunEffectsBurialSand1996}. The stresses signal of gravity signal in complete sand burial was usually stronger than it in half sand burial \citep{wangAdvancesStudiesMorphological2005}. This was consistent with our field investigation, we found that the tall remets of \textit{S. littoreus} could intercept sand sediments, and its conjoint stolons were buried at different levels on nebkhas. The stolon length of \textit{S. littoreus} on nebkhas in developmental period was much longer than it in stabilized period, which can be attributed to the more dynamic sand movement on the fomer (Figure~\ref{fig:added}).

@@

% 凭借上述机制，我们的结果表明老鼠楽能够有效在近地表被严重的沙埋情况下加速生长并存活下来。在热带和亚热带地区的海岸，频繁的台风常常为迎风坡带来数十厘米厚的沙埋，尽管这样的沙埋足以阻止大多数植物在此生长，但老鼠楽凭借其独特的适应能力在此占据来绝对优势。
Response of plants to sand burial is usually species specific, and the growth of plants will be enhanced under optimal sand burial rate \citep{noletUAVimagingModelGrowth2018}. We found that \textit{S.littoreus} can adapt to the severe sand burial caused by frequent typhoons in our study area, and will revitalize later by increasing the horizontal stolon length, producing abundant adventitious roots on the stolon base and allocating more biomass to leaves on the stolon apex \citep{yuanEffectsSandAccretion1993}. However, if the sand burial rate is over some threshold, the growth of sand dune species will be inhibited \citep{maunEffectsBurialSand1996, shiEffectsSandBurial2004}. Our field investigation showed that few \textit{S. littoreus} can be found on the leeward slope of nebkhas (Figure~\ref{fig:leeward_swale}a), which can be attributed to the excessive sand burial on both ramets and conjoint stolons of \textit{S. littoreus}. Absence of photosynthesis area, combined with the continuous depletion of reserves previously stored in the plants \citep{frosiniGlobalChangeResponse2012}, finally lead to the failure of \textit{S. littoreus} escaped from excessive sand burial on leeward slope of nebkhas (Figure~\ref{fig:leeward_swale}a).  Similarly, if the sand burial rate is below some threshold, the species that can not withstand the severe sand burial will co-occur with those resistant to it. We found that low to moderate sand burial treatments had no significant impact on the stolon extension of \textit{S.littoreus}, which will not favor its access to the more habitats for soil water and nutrition, and further weaken its advantages as the dominant species with the decrease of sand burial rate. This is also consistent with our field investigation, \textit{Oenothera drummondii}, which is more frequently occurred on the nebkhas stabilized by \textit{C. equisetifolia}, an invasive species widely distributed on the stabilized dune in South China, was co-occurred with \textit{S.littoreus} on the less dynamic nebkhas in our study area (Figure~\ref{fig:added}a).

@@

\begin{figure}
  \centering
  \subfloat[Leeward.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/leeward.jpg}}}\hspace{5pt}
  \subfloat[Swale.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/swale.jpg}}}
  \caption{(a) Leeward is the most severe sand-burial position where few plants can survive there, including \textit{S. littoreus}. (b) Swales are much better habitats for plants because of little sand burial. However, \textit{S. littoreus} can not be dominant in this area because of heavy competition.} 
  \label{fig:leeward_swale}
\end{figure}

@@

(3) \textit{S. littoreus} can adapt to the intense sand burial in growing season by rapid growth of stolons, it can be considered as one of the optimal species for stabilizing and building the coastal sand dunes in South China.

>>>>

\documentclass[]{interact}
\usepackage{lineno}
\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required

@@

\linenumbers
\articletype{ARTICLE}% Specify the article type or omit as appropriate

@@

\begin{abstract}
\label{abstract}
% 砂生植物对沙埋藏的适应能力对海岸沙丘系统的生态恢复至关重要。
The adaptive capacity of psammophytes to sand burial is crucial for the ecological restoration of coastal dune systems. 
% 研究了福建平潭岛海岸滨鹬对不同埋沙深度和埋沙深度的响应。
The responses of \textit{Spinifex littoreus} to different sand burial depths and levels were examined on the coast of Pingtan Island, Fujian Province, South China. 
% 结果表明，与对照组相比，砂埋对其匍匐茎的垂直生长无显著影响。
The results indicated that, compared with the control group (CG), sand burial on the \textit{S. littoreus} stolons had no significant impact on the vertical growth of its conjoint ramets. 
% 然而，随着砂埋的继续，匍匐茎顶端生长更快，完全砂埋比半砂埋影响更明显。
However, the horizontal growth of \textit{S. littoreus} stolons were stimulated and significantly increased in half-intense (HI) and complete-intense (CI) sand burial treatments by 24.56\% and 40.79\%, respectively. 
% 在不定根和叶片上，三个匍匐茎上的干生物量分配均发生了变化，而在茎上则没有变化。
Throughout the experiment, about 96\% of adventitious roots were observed on the base section of stolons, while no roots in the control group (CG). 
After 20-day artificial sand burial treatments, the dry weight ratio between stem and leaf of \textit{S. littoreus} was decreased in all three sections of stolons, especially for the top sections. 
% 通过匍匐茎的快速生长，匍匐茎基部产生大量不定根，匍匐茎顶端的叶片萌发率较高，可以适应完全的砂埋。
Overall, \textit{S. littoreus} can adapt to the complete and intense sand burial in growing season by rapid growth of stolons, abundant production of adventitious roots on the stolon base, and more germination of leaves on the stolon top.
\end{abstract}

@@

\subsection{Methods}
Field experiments were carried out in July, 2016, in Tannan bay, Pingtan Island (Figure~\ref{fig:map}). One study belt without the interruption of animals, pollutants, and apparent human activities was selected in the center of the coastal sand dunes. 
Considering most of the \textit{S. littoreus} were distributed on the windward slope of nebkhas in mobile dunes belt, 35 healthy plants with uniform size were selected for study on this slope (Figure\ref{fig:leeward_swale}). All the observed plants can be well distinguished from surrounding plants, the height of vertical ramets and the length of stolons were all similar with each other before the burial treatments. Stolons of \textit{S. littoreus} on the windward slopes were selected, and labeled with a red cord at points 1/3 and 2/3 of the length from the stem base to the top of the stolons. All plant species around the selected plants were manually cleared, and wooden frames $20 cm$ in height (similar to the height of stolons) were set around the selected plants. Later, all the observed plants were fixed with a label, and its serial number was recorded on the label and wooden baffles respectively in order to facilitate the periodic measurements later. The few adventitious roots present on the stolons of the observed plants were completely eliminated, the height of vertical ramets and length of stolons were measured separately before the experiments began. Later, all the plants were buried with sand nearby artificially (Figure~\ref{fig:diagram}, Table~\ref{tab:treatment}), While control groups (CG) were unburied throughout the experiments.

@@

Since the vertical ramets of \textit{S. littoreus} is relatively high, it is unlikely for them to be completely buried in a single typhoon event (Figure~\ref{fig:sample-pic}a). The treated \textit{S. littoreus}, thus, only the stolons of which were buried at different depths and levels (see Figure~\ref{fig:diagram} and Table~\ref{tab:treatment}). Moreover, some adventitious roots on the stolons of selected plants were observed only a few days after treatments, so the growth parameters of plants were dynamically investigated in 5, 9, 13, 17, 20 days after the sand burial to investigate the response of \textit{S. littoreus} to severe sand burial over a short time scale.

@@

Consequently, the rapid growth of ramets height in \textit{S. littoreus} is not considered as the priority for the escape of sand burial, but it inclines to increase the stolon length due to its vulnerability to be buried in a typhoon event, which may contribute to the no significant impact on the ramets height by artificial sand burial in our experiment \citep{maunAdaptationsEnhancingSurvival1994}. Our field investigation further showed that the maximum length of \textit{S.littoreus} stolons could be up to $2-3 m$, which was about to 4-6 times of its ramets height in a frequent sand burial habitat (Figure~\ref{fig:added}b). This is in agreement to the previous study from \citet{woodhouseEffectSpeciesDune1977}, who reported that \textit{Uniola paniculata} tended to grow upward rather than seaward, while \textit{Ammophila breviligulata} preferred to colonize seaward beach surfaces by rhizome growth, which may explain the wider distribution of the latter in an intensive sand burial environment subsequently.

\begin{figure}[!h]
  \centering
  \subfloat[Developmental period.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9a.jpg}}}\hspace{5pt}
  \subfloat[Stabilized period.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9b.jpg}}}
  \caption{The stolon length of \textit{S. littoreus} on nebkhas in the developmental period (a) and the stabilized period (b). (Photo was taken in Pingtan Island)} 
  \label{fig:added}
\end{figure}

Extensive colonization of horizontal stolons after sand burial will facilitate the plants to increase its capacity for utilization of water and nutrition, which is especially critical for the establishment of plants in a resource-poor environment, such as coastal sand dunes, and further enhance their growth as the dominant species in coastal sand dunes \citep{divyasreeEcologicalStudyReproduction2019,mendoza-gonzalezBiologicalFloraCoastal2014}. Our results indicated that all sand burial treatments had a significant promotion on the  stolon growth, and complete sand burial had more obvious influence than half sand burial. Species usually stimulate their growing point according to the signal of the gravity signal stresses \citep{zhouAnalysisgrowthstrategy2015}, and increase their node number and internode length to escape this physical barrier \citep{maunEffectsBurialSand1996}. The stresses signal of gravity signal in complete sand burial was usually stronger than it in half sand burial \citep{wangAdvancesStudiesMorphological2005}. This was consistent with our field investigation, we found that the tall remets of \textit{S. littoreus} could intercept sand sediments, and its conjoint stolons were buried at different levels on nebkhas. The stolon length of \textit{S. littoreus} on nebkhas in developmental period was much longer than it in stabilized period, which can be attributed to the more dynamic sand movement on the fomer (Figure~\ref{fig:added}).

@@

% 凭借上述机制，我们的结果表明老鼠楽能够有效在近地表被严重的沙埋情况下加速生长并存活下来。在热带和亚热带地区的海岸，频繁的台风常常为迎风坡带来数十厘米厚的沙埋，尽管这样的沙埋足以阻止大多数植物在此生长，但老鼠楽凭借其独特的适应能力在此占据来绝对优势。
Response of plants to sand burial is usually species specific, and the growth of plants will be enhanced under optimal sand burial rate \citep{noletUAVimagingModelGrowth2018}. We found that \textit{S.littoreus} can adapt to the severe sand burial caused by frequent typhoons in our study area, and will revitalize later by increasing the horizontal stolon length, producing abundant adventitious roots on the stolon base and allocating more biomass to leaves on the stolon apex \citep{yuanEffectsSandAccretion1993}. However, if the sand burial rate is over some threshold, the growth of sand dune species will be inhibited \citep{maunEffectsBurialSand1996, shiEffectsSandBurial2004}. Our field investigation showed that few \textit{S. littoreus} can be found on the leeward slope of nebkhas (Figure~\ref{fig:leeward_swale}a), which can be attributed to the excessive sand burial on both ramets and conjoint stolons of \textit{S. littoreus}. Absence of photosynthesis area, combined with the continuous depletion of reserves previously stored in the plants \citep{frosiniGlobalChangeResponse2012}, finally lead to the failure of \textit{S. littoreus} escaped from excessive sand burial on leeward slope of nebkhas (Figure~\ref{fig:leeward_swale}a).  Similarly, if the sand burial rate is below some threshold, the species that can not withstand the severe sand burial will co-occur with those resistant to it. We found that low to moderate sand burial treatments had no significant impact on the stolon extension of \textit{S.littoreus}, which will not favor its access to the more habitats for soil water and nutrition, and further weaken its advantages as the dominant species with the decrease of sand burial rate. This is also consistent with our field investigation, \textit{Oenothera drummondii}, an invasive species widely distributed on the stabilized dune in South China, is more frequently co-occurred with \textit{S.littoreus} on the nebkhas stabilized by \textit{C. equisetifolia} in our study area (Figure~\ref{fig:added}a).

@@

\begin{figure}
  \centering
  \subfloat[Leeward.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/leeward.jpg}}}\hspace{5pt}
  \subfloat[Swale.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/swale.jpg}}}
  \caption{(a) Leeward is the most severe sand-burial position where few plants can survive there, including \textit{S. littoreus}. (b) Swales are much better habitats for plants because of little sand burial. However, \textit{S. littoreus} can not be dominant in this area because of heavy competition. Photo was taken in Pingtan Island.} 
  \label{fig:leeward_swale}
\end{figure}

@@

(3) \textit{S. littoreus} can adapt to the severe sand burial in growing season, it can be considered as one of the optimal species for stabilizing and building the coastal sand dunes in South China.
